---
bibliography: biib.bib
csl: ecology.csl
output: pdf_document
---

```{r packages, echo=F, message=F, warning=F}
# need my R package?
#library(devtools)
#install_github("aurielfournier/rel")


library(gridExtra)
library(reshape2)
library(reshape)
library(xtable)
library(ggplot2)
library(jpeg)
library(grid)
library(auriel)
library(chron)

img <- readJPEG("./20150908_192206.jpg")
grid.raster(img)


```

\huge RAILS ARE AWESOME

\Large Progress Report 2015 

\Large Auriel M.V. Fournier 

\newpage

So you can type text here and talk about how cool rails are. Discussing other things is not possible. Only rails. 

You can also cite my cool papers on rails [@Fournier2013, @Fournier2015b]. You can also cite my editorial about the issue of unpaid work in ecology [@Fournier2015a]. 

\newpage

# Fun with Graphs

```{r, echo=F, message=F, warning=F}

dat <- read.csv('../step_1/example_survey_data.csv')

mdat <- melt(data=dat[,c("jdate","sora")], id=c("jdate"))
cdat <- cast(data=mdat, jdate ~ variable, median)

ggplot(data=cdat)+geom_bar(aes(x=jdate, y=sora), stat="identity")+theme_krementz()+scale_x_ordinaldate(year=2015)+xlab("date")+ylab("sora per hectare")


```



\newpage

# Citations
